TITLE

### 2021-02-26 outputs/Paper.Rmd
update

* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor. From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group. We assume in treated group, the branch franchise restaurants should follow the rules by the head office. Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.

(Figure \@ref(fig:pie1))

```{r pie1, fig.cap = "Restaurant franchise distribution",echo=FALSE, fig.width=10, fig.height=4}

@@

#Merge twp graphs
ggarrange(
  Pie1, Pie2, 
  ncol = 2, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )
```
* The polar chart illustrates the employee numbers distribution, as can be seen in figure 5. (Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in. So in the control group, there is 0 restaurant which has more than 30 employees. Most of restaurant has 10 to 20 employees.

@@

### Invention effect on Revenue distributions

```
Two merged histograms charts were used to illustrate the restaurant's revenue distribution.

(Figure \@ref(fig:revenue_distribution))

### Invention effect on Flex and fiexed cost

### Correlation matrix
```{r correlation, fig.cap = "Correlation matrix",echo=FALSE, fig.width=20, fig.height=10}
#install.packages("fastDummies")
library(fastDummies)
Dummy_data<-treated_data[-c(1,2)] #Remove Type and postcode columns

@@

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot1 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )

# correlation matrix for restaurants in control group
Dummy_data<-control_data[-c(1,2)] #Remove Type and postcode columns

Dummy_data<-Dummy_data[-c(1:3,5:7,9:11,13,44)]

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot2 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )
# combine two diagram in one graph

ggarrange(
  corr.plot1, corr.plot2, 
  labels = c('Treated group', 'Control group'),
  ncol = 2, nrow = 1,
  align = "hv"
  )

@@

### Finding TWO

### Finding THREE

## Limitation

>>>>

* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor. From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group. We assume in treated group, the branch franchise restaurants should follow the rules by the head office. Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.
(Figure \@ref(fig:pie1))

```{r pie1, fig.cap = "Restaurant franchise distribution", echo=FALSE, fig.width=10, fig.height=4}

@@

#Merge twp graphs
ggarrange(
  Pie1, Pie2, 
  ncol = 2, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )
```
* The polar chart illustrates the employee numbers distribution, as can be seen in figure below. (Figure \@ref(fig:employee)) Because of COVID rule, no restaurant is allowed to open for large group dine in. So in the control group, there is 0 restaurant which has more than 30 employees. Most of restaurant has 10 to 20 employees.

@@

### Correlation matrix
Correlation matrix shows internal relationships between x variables and y variable. (Figure \@ref(fig:correlation)) Intensity is indicated by the color(from red to blue). No significant coeffiency   is barred with symbol "x". More detailed analysis will be conducted in finding part.

```{r correlation, fig.cap = "Correlation matrix",echo=FALSE, fig.width=10, fig.height=10}
#install.packages("fastDummies")
library(fastDummies)
Dummy_data<-simulated_data[-c(1,2)] #Remove Type and postcode columns

@@

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat,
  title = "Correlation Matrix"
  )

@@

### Finding TWO
Invention effect on Flex and fiexed cost

```
### Finding THREE
Invention effect on Revenue distributions

```
## Limitation
